---
title: 'Status of the Rougheye and Blackspotted Rockfishes stock off the U.S. West Coast in 2025'
author:
  - name: 'Jason M. Cope'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
  - name: 'Vladlena Gertseva'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
  - name: 'R. Claire Rosemond'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2032 SE OSU Drive'
        city: 'Newport, OR'
        state: 'OR'
        postal-code: '97365-5275'
  - name: 'Alison D. Whitman'
    affiliations:
      - name: 'Oregon Department of Fish and Wildlife'
        address: '2040 Southeast Marine Science Drive'
        city: 'Newport, OR'
        state: 'OR'
        postal-code: '97365'
  - name: 'Fabio P. Caltabellotta'
    affiliations:
      - name: 'Washington Department of Fish and Wildlife'
        address: '48 Devonshire Road'
        city: 'Montesano, WA'
        state: 'WA'
        postal-code: '98563'
date: today
lang: en 
keep-tex: true 
cover: REBS.png
pdf-engine: lualatex
format: 
  pdf: 
    documentclass: article
    number-sections: true
    template-partials:
      - 'support_files/before-body.tex'
      - 'support_files/_titlepage.tex'
    include-in-header:
      - 'support_files/in-header.tex'
      - 'support_files/pfmc.tex'
    toc: false
    lof: false
    lot: false
    titlepage-geometry: 
      - top=2in
      - bottom=1in
      - right=1in
      - left=1in
    link-citations: true
    fig-pos: 'H'
output-file: 'Rougheye_and_Blackspotted_Rockfishes_SAR_2025' 
params:
   office: 'NWFSC'
   species: 'Rougheye and Blackspotted Rockfishes'
   spp_latin: 'Sebastes aleutianus'
   region: 'U.S. West Coast'
bibliography: 
-  asar_references.bib
csl: 'canadian-journal-of-fisheries-and-aquatic-sciences.csl'
---

```{r, results='asis'}
#| label: 'load_packages'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('001_load_packages.qmd', quiet = TRUE)
cat(a, sep = '\n')
```


```{r} 
#| label: 'output_and_quantities'
#| echo: false 
#| warning: false 
#| eval: true 

library(here)

spp <- "Rougheye/Blackspotted rockfishes"
Spp <- "Rougheye/Blackspotted rockfishes"
Spp_short<- "RE/BS"

#Main model directory
#model_dir <- here::here("model", "_bridging", model_name)
model_dir <- file.path(here::here('Document','report','ref_model'))
plot_dir<- file.path(here::here('Document','report','plots_4_doc'))
sens_dir <- file.path(here::here('Document','report','Sensis'))
retro_dir <- file.path(here::here('Document','report','Retros'))
like_dir <- file.path(here::here('Document','report','Like_profiles'))

#Table directory
table_dir <- file.path(model_dir, "tables")

model_output <- r4ss::SS_output(model_dir,verbose=FALSE,printstats=FALSE)

#decision table
source(here::here('Rcode/decision_table.R'))

# load converted output from asar::convert_output() 
#output <- utils::read.csv('C:/Users/Jason.Cope/Documents/Github/REBS-2025/Document/update/reye_blkspt_convert_#output.csv') 
# Call reference points and quantities below 
# output <- output |> 
#   dplyr::mutate(estimate = as.numeric(estimate), 
#     uncertainty = as.numeric(uncertainty)) 
# start_year <- as.numeric(min(output$year, na.rm = TRUE)) 
# end_year <- (output |> 
#   dplyr::filter(!(year %in% c('Virg', 'Init', 'S/Rcurve', 'INIT')), 
#     !is.na(year)) |> 
#   dplyr::mutate(year = as.numeric(year)) |> 
#   dplyr::summarize(max_val = max(year)) |> 
#   dplyr::pull(max_val))-10
# # subset output to remove quantities that are split by factor 
# output2 <- output |> 
#   dplyr::filter(is.na(season), 
#     is.na(fleet), 
#     is.na(sex), 
#     is.na(area), 
#     is.na(growth_pattern), 
#     is.na(subseason), 
#     is.na(age))
# # terminal fishing mortality 
# Fend <- output2 |> 
#   dplyr::filter(c(label == 'fishing_mortality' & year == end_year) | c(label == 'terminal_fishing_mortality' & is.na(year))) |>
#   dplyr::pull(estimate)
# # fishing mortality at msy 
# # please change target if desired 
# Ftarg <- output2 |>
#   dplyr::filter(grepl('f_target', label) | grepl('f_msy', label) | c(grepl('fishing_mortality_msy', label) & is.na(year))) |>
#   dplyr::pull(estimate)
# # Terminal year F respective to F target 
# F_Ftarg <- Fend / Ftarg
# # terminal year biomass 
# Bend <- output2 |>
#   dplyr::filter(grepl('mature_biomass', label) | grepl('^biomass$', label),
#     year == end_year) |>
#   dplyr::pull(estimate)
# # target biomass (msy) 
# # please change target if desired 
# Btarg <- output2 |>
#   dplyr::filter(c(grepl('biomass', label) & grepl('target', label) & estimate >1) | label == 'biomass_msy') |>
#   dplyr::pull(estimate)
# # total catch in the last year 
# total_catch <- output |>
#   dplyr::filter(grepl('^catch$', label), 
#   year == end_year,
#     is.na(fleet),
#     is.na(age),
#     is.na(area),
#     is.na(growth_pattern)) |>
#   dplyr::pull(estimate)
# # total landings in the last year 
# total_landings <- output |>
#   dplyr::filter(grepl('landings_weight', label), year == end_year,
#     is.na(fleet),
#     is.na(age)) |>
#   dplyr::pull(estimate)
# # spawning biomass in the last year
# sbend <- output2 |>
#   dplyr::filter(grepl('spawning_biomass', label), year == end_year) |>
#   dplyr::pull(estimate) |>
#     unique()
# #Terminal year stock status
# stock.status.current<-output[output$label=="biomass_ratio",2][length(output[output$label=="biomass_ratio",2])]
# # overall natural mortality or at age 
# M <- output |>
#   dplyr::filter(grepl('natural_mortality', label)) |>
#   dplyr::pull(estimate)
# # Biomass at msy 
# # to change to another reference point, replace msy in the following lines with other label 
# Bmsy <- output2 |>
#   dplyr::filter(c(grepl('biomass', label) & grepl('msy', label) & estimate >1) | label == 'biomass_msy') |>
#   dplyr::pull(estimate)
# # target spawning biomass(msy) 
# # please change target if desired 
# SBtarg <- output2 |>
#   dplyr::filter(c(grepl('spawning_biomass', label) & grepl('msy$', label) & estimate >1) | label == 'spawning_biomass_msy$') |>
#   dplyr::pull(estimate)
# # steepness 
# h <- output |> 
#   dplyr::filter(grepl('steep', label)) |> 
#   dplyr::pull(estimate)
# # recruitment 
# R0 <- output |> 
#   dplyr::filter(grepl('R0', label) | grepl('recruitment_virgin', label)) |> 
#   dplyr::pull(estimate)
# # female SB (placeholder)

``` 


{{< pagebreak >}} 

Please cite this publication as: 

Cope, J.M., V. Gertseva, R.C. Rosemond, A.D. Whitman, and F.P. Caltabellotta. (2025) Status of the Rougheye and Blackspotted Rockfishes stock off the U.S. West Coast in 2025. Pacific Fishery Management Council. 356 pp.

 {{< pagebreak >}} 


 <!-- This includes the two-pagers at the top of the executive summary -->

 \clearpage
\thispagestyle{empty}
\noindent
\begin{tikzpicture}[remember picture, overlay]
    \node[inner sep=0pt, anchor=north west] 
    at (current page.north west) {
        \includegraphics[width=8.5in, height=11in, alt={Stock assessment summary graphic with figures total removals, spawning output and relative stock size time series. It also includes a table of projected catches and key takeaways.}]{plots_4_doc/AAG_page1.png}
    };
\end{tikzpicture}
\clearpage
\thispagestyle{empty}
\begin{tikzpicture}[remember picture, overlay]
    \node[inner sep=0pt, anchor=north west] 
    at (current page.north west) {
        \includegraphics[width=8.5in, height=11in, alt={Stock assessment summary graphic that contains a comparison of data sources and model outputs from the current stock assessment to the 2013 stock assessment.}]{plots_4_doc/AAG_page2.png}
    };
\end{tikzpicture}
\clearpage

 
```{r, results='asis'}
#| label: 'load_tables'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('002_load_tables.qmd', quiet = TRUE)
cat(a, sep = '\n')
```


```{r, results='asis'}
#| label: 'disclaimer'
#| eval: false
#| echo: false
#| warning: false
a <- knitr::knit_child('00a_disclaimer.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 


\hypersetup{linkcolor=.}
\setcounter{tocdepth}{3}
\tableofcontents

{{< pagebreak >}}
 
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}

\setlength\parskip{0.5em plus 0.1em minus 0.2em}


```{r, results='asis'}
#| label: 'visual_summary'
#| eval: false
#| echo: false
#| warning: false
a <- knitr::knit_child('003_visual_summary.qmd', quiet = TRUE)
cat(a, sep = '\n')
```


 {{< pagebreak >}} 


```{r, results='asis'}
#| label: 'executive_summary'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('01_executive_summary.qmd', quiet = TRUE)
cat(a, sep = '\n')
```


 {{< pagebreak >}} 

\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\setcounter{section}{0}
\renewcommand{\thefigure}{\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}



```{r, results='asis'}
#| label: 'introduction'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('02_introduction.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'data'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('03_data.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-configuration'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04a_assessment-configuration.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-results'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04b_assessment-results.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-sensitivity'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04c_assessment-sensitivity.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'management'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('05_management.qmd', quiet = TRUE)
cat(a, sep = '\n')
```
 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'acknowledgments'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('06_acknowledgments.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'references'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('07_references.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'tables'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('08_tables.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'figures'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('09_figures.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'notes'
#| eval: false
#| echo: false
#| warning: false
a <- knitr::knit_child('10_notes.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'appendix'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('11_appendix.qmd', quiet = TRUE)
cat(a, sep = '\n')
```
